### 2016-11-21 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
eds

**Table1**
```{r Table 1}

CIs <- CIwald(RTL_Full)
t1 <- data.frame(Estimate = fixef(RTL_Full), LCI = CIs[6:nrow(CIs),1], UCI = CIs[6:nrow(CIs),2])
kable(t1)

@@

temp <- subset(dd3,!is.na(Insect))

#Run the model
CIs <- CIwald(DeltaRTL_Full)
t1 <- data.frame(Estimate = fixef(DeltaRTL_Full), LCI = CIs[4:nrow(CIs),1], UCI = CIs[4:nrow(CIs),2])
kable(t1)

@@

Fig1 <- ddply(dd,
               .(BirdID),
        mutate,
        nreps = length(RTL)) %>%
  subset(nreps>0) %>%
  subset(!duplicated(paste0(BirdID,Agemonths))) %>%
  ggplot(aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))
  annotate('text',x = 0,y = 3,label = 'A')

pdf('Figures/Figure 1.pdf',
    width = 4,
    height = 4,
    paper = 'a4')
Fig1
dev.off()

@@

Fig2A <- transform(juv,Cohort = factor(CatchYear)) %>%
  subset(Agemonths>(1/12)) %>%
  ggplot(aes(y = RTL,x = Cohort))+
  xlab('Cohort') +
  geom_boxplot() +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

Fig2B <- transform(dd,Cohort = factor(CatchYear)) %>%
  ddply(.(Cohort),
        mutate,
        nc = length(which(Agemonths ==1/12))) %>%
  subset(nc > 11) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~log(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

pdf('Figures/Figure 2.pdf',
    width = 5,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B)
dev.off()

@@

Fig3A <- ggplot(dd3,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 3,label = 'B')

Fig3B <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)
  annotate('text',x = -2,y = 1,label = 'C')

pdf('Figures/Figure 3.pdf',
    width = 5,
    height = 8,
    paper = 'a4')
multiplot(Fig3A,Fig3B)
dev.off()

@@

Fig4A <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm')
  annotate('text',x = 17,y = 2.5,label = 'C')

Fig4B <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')
  annotate('text',x = 2.5,y = 2.5,label = 'D')

>>>>

**Table 1**
```{r Table 1}

AIC(RTL_LogAge)
AIC(RTL_LogAge_LY)

**Table 2**
```{r Table 2}

CIs <- CIwald(RTL_Full)
t1 <- data.frame(Estimate = fixef(RTL_Full), LCI = CIs[7:nrow(CIs),1], UCI = CIs[7:nrow(CIs),2])

nams <- row.names(t1)
nams[nams == 'LogAge'] <- 'Age'
nams[nams == 'Tarsus'] <- 'Tarsus length'
nams[nams == 'Helper'] <- 'Number helpers'
nams[nams == 'GroupSize'] <- 'Group size'
nams[nams == 'SexMales'] <- 'Sex (males)'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'Insect'] <- 'Annual food availability'
nams[nams == 'TQ'] <- 'Territory quality'

row.names(t1) <- nams

kable(t1)

@@

#Run the model
CIs <- CIwald(DeltaRTL_Full)
t1 <- data.frame(Estimate = fixef(DeltaRTL_Full), LCI = CIs[4:nrow(CIs),1], UCI = CIs[4:nrow(CIs),2])

nams <- row.names(t1)
nams[nams == 'LogAge'] <- 'Age'
nams[nams == 'Tarsus'] <- 'Tarsus length'
nams[nams == 'Helper'] <- 'Number helpers'
nams[nams == 'GroupSize'] <- 'Group size'
nams[nams == 'SexMales'] <- 'Sex (males)'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'Insect'] <- 'Annual food availability'
nams[nams == 'TQ'] <- 'Territory quality'

row.names(t1) <- nams

kable(t1)

@@

Fig1A <- ddply(dd,
               .(BirdID),
        mutate,
        nreps = length(RTL)) %>%
  subset(nreps>0) %>%
  subset(!duplicated(paste0(BirdID,Agemonths))) %>%
  ggplot(aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))+
  annotate('text',x = 0,y = 1.7,label = 'A')

  Fig1B <- ggplot(dd3, aes(x = DeltaAge,y = RTL))+
  geom_point(alpha = 1,col='grey')+
  xlab(expression(Delta*'Age (years)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',method = 'lm')+
  annotate('text',x = -7.5,y = 1.7,label = 'B')

pdf('Figures/Figure 1.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig1A,Fig1B)
dev.off()

```{r Figure 2}
c15 <- c("dodgerblue2","#E31A1C", # red
                "green4",
                "#FF7F00", # orange
                "gold1",
                "skyblue2", # lt pink
                "palegreen2",
                "#FDBF6F", # lt orange
                "gray70", "khaki2","blue1","steelblue4",
                "darkturquoise",
                "darkorange4","brown")

Fig2A <- transform(dd,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Cohort,fill = Cohort))+
  xlab('Birth year') +
  geom_boxplot(notch=T) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.7,label = 'A')

Fig2B <- transform(dd,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~log(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'B')

Fig2C <- transform(dd,Cohort = factor(CatchYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Cohort,fill = Cohort))+
  xlab('Sampling year') +
  geom_boxplot(notch=T) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') + 
    scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.7,label = 'C')

Fig2D <- transform(dd,Cohort = factor(CatchYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~log(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'D')

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B,Fig2C,Fig2D,layout = matrix(1:4, 2, 2,byrow = T))
dev.off()

@@

c15 <- c("dodgerblue2","#E31A1C", # red
                "green4",
                "#FF7F00", # orange
                "gold1",
                "skyblue2", # lt pink
                "palegreen2",
                "#FDBF6F", # lt orange
                "gray70", "khaki2","blue1","steelblue4",
                "darkturquoise",
                "darkorange4","brown")

Fig2A <- transform(dd,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Cohort,fill = Cohort))+
  xlab('Birth year') +
  geom_boxplot(notch=T) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.7,label = 'A')

Fig2B <- transform(dd3,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = DeltaAge, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'B')

Fig2C <- transform(dd,Cohort = factor(CatchYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Cohort,fill = Cohort))+
  xlab('Sampling year') +
  geom_boxplot(notch=T) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') + 
    scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.7,label = 'C')

Fig2D <- transform(dd,Cohort = factor(CatchYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = DeltaAge, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'D')

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B,Fig2C,Fig2D,layout = matrix(1:4, 2, 2,byrow = T))
dev.off()

@@

Fig3A <- ggplot(dd3,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2) +
  annotate('text',x = 0.3,y = 1.7,label = 'A')

Fig3B <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2) +
  annotate('text',x = -1,y = 1,label = 'B')

pdf('Figures/Figure 3.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig3A,Fig3B)
dev.off()

@@

Fig4A <- ggplot(dd,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm') +
  scale_color_manual(values = c('gold2','red'))+
  annotate('text',x = 17,y = 1.7,label = 'A')

Fig4B <- ggplot(dd,
       aes(y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey') +
  annotate('text',x = 2.5,y = 1.6,label = 'B')
